Coupling finite and boundary element methods to solve the Poisson--Boltzmann equation for electrostatics in molecular solvation

### 2023-05-09 main.tex
TB acknowledgement

\subsection*{\sffamily \large ACKNOWLEDGMENTS}
MB acknowledges the support from Kingston University through First Kingston University Grant. \\
CDC acknowledges the support from CCTVal through ANID PIA/APOYO AFB220004.\\
MS acknowledges support from EPSRC grant EP/W007460/1 \\
EB acknowledges support from EPSRC grants EP/V050400/1 and EP/W007460/1 \\
We would like to thank J{\o}rgen Dokken for his help with various implementation details related to FEniCSx.
%((Place Acknowledgments here))

>>>>

\subsection*{\sffamily \large ACKNOWLEDGMENTS}
MB acknowledges the support from Kingston University through First Kingston University Grant. \\
MS acknowledges support from EPSRC grant EP/W007460/1 \\
TB acknowledges support from EPSRC grants EP/W007460/1 and EP/W026260/1. \\
EB acknowledges support from EPSRC grants EP/V050400/1 and EP/W007460/1. \\
CDC acknowledges the support from CCTVal through ANID PIA/APOYO AFB220004.\\
We would like to thank J{\o}rgen Dokken for his help with various implementation details related to FEniCSx.
%((Place Acknowledgments here))
